\documentclass{article}
%--Packages------------
\usepackage{fancyvrb}
\usepackage{alltt}

%----------------------

%--Variables-----------
\newcommand{\AssignmentNum}{2}
\newcommand{\QuestionNum}{1}
\newcommand{\AssignmentTitle}{Are you satised with Constraint Satisfaction?}
\newcommand{\AssignmentDate}{\today}
%----------------------

%--Title & Author------
\title{CMPT 317, Term 2, 2013\\
Assignment \AssignmentNum\\
Question \QuestionNum\\
\AssignmentTitle
}
\author{
	\begin{tabular}{ l r }
	  Name: & Quinn Neumiiller \\
	  NSID: & qjn162 \\
	  Student \# & 11065618 \\
	\end{tabular}
}
\date{\AssignmentDate}
%----------------------

%--Document------------
\begin{document}
   \maketitle
   
   \section{Compiling}
   Not required for Python

   \section{Execution}
   To execute, change the terminal directory to where this PDF file sits.
   Then in the terminal execute:
	\begin{alltt}
	python src/Q\QuestionNum.py
	\end{alltt}

  \section{Usage}
    No usage required, script is self automated
  \section{Explanation}
    The script will take in the Midterm\_Constraints.txt and it already knows about the domains.

    It will go from 0 till 100 trying to find acceptable domains given the constraints.

    It will range from Domain-N to Domain+N, if the constraint is found in that range the
    Domain is removed as a acceptable domain.

    The program continues until there is no more successful answers, at that point it will grab the previous
    set of acceptable answers and print them out.

    NOTE: for ease of comparison I've transformed all dates into the day of year they represent
    Ex) March 11 == 70th day of the year

    I convert the accepted dates back into their string representation for reading.
  \section{Answer}
    According to the script, March 11th (70th day of the year) is the highest accepted 
    date between constraints and is the day of the Midterm

  \section{Suggestions}
    I really really liked the idea of this question when posted, although it would be much cooler
    if we could enter in our own constraints (ex: other midterms scheduled) and try find our most
    acceptable midterm date out of the Domains provided. Obviously majority gets the midterm date of their chosing.

\end{document}
%----------------------

